### 2019-11-29 monograph/aftertext/appendices.tex
Moved the main_formatter and highlighter output examples into
separate files main_formatter_output.txt and main_highlighter_output.txt

\begin{code}
\caption{Resultado da execução do arquivo ``source/main\_formatter.py''}
\label{MainFormatterPyResult}
\begin{minted}{text}
$ python3 main_formatter.py
Syntax Tree
language_syntax
  preamble_statements
    master_scope_name_statement
      free_input_string
        text_chunk_end  [@1,7:16='source.sma'<TEXT_CHUNK_END_>,1:8]
    target_language_name_statement
      free_input_string
        text_chunk_end  [@2,24:48='Abstract Machine Language'<TEXT_CHUNK_END_>,2:7]
  language_construct_rules
    indentation_block
      enter_block       [@3,60:60='{'<OPEN_BRACE>,3:11]
      statements_list
        match_statement
          braced_free_input_string
            braced_text_chunk_end       [@4,73:76='if\\('<BRACED_TEXT_CHUNK_END_>,4:12]
          statements_list
            scope_name_statement
              free_input_string
                text_chunk_end  [@5,95:117='if.statement.definition'<TEXT_CHUNK_END_>,5:16]
          statements_list
            push_statement
              indentation_block
                enter_block     [@6,133:133='{'<OPEN_BRACE>,6:15]
                statements_list
                  meta_scope_statement
                    free_input_string
                      text_chunk_end    [@7,159:175='if.statement.body'<TEXT_CHUNK_END_>,7:25]
                statements_list
                  match_statement
                    braced_free_input_string
                      braced_text_chunk_end     [@8,196:197='\\)'<BRACED_TEXT_CHUNK_END_>,8:20]
                    statements_list
                      scope_name_statement
                        free_input_string
                          text_chunk_end        [@9,224:246='if.statement.definition'<TEXT_CHUNK_END_>,9:24]
                    statements_list
                      pop_statement
                        free_input_string
                          text_chunk_end        [@10,269:272='true'<TEXT_CHUNK_END_>,10:22]
                leave_block     [@11,296:296='}'<CLOSE_BRACE>,12:9]
      leave_block       [@12,304:304='}'<CLOSE_BRACE>,14:1]

Abstract Syntax Tree
language_syntax
  preamble_statements
    master_scope_name_statement InputString str: , is_out_of_scope: [], chunks: [source.sma], definitions: {}, errors: [], indentations: [<indent 2, open 133, close 296>, <indent 1, open 60, close 304>], is_resolved: False;
    target_language_name_statement      InputString str: , is_out_of_scope: [], chunks: [Abstract Machine Language], definitions: {}, errors: [], indentations: [<indent 2, open 133, close 296>, <indent 1, open 60, close 304>], is_resolved: False;
  language_construct_rules
    indentation_block
      statements_list
        match_statement
          InputString str: if\(, is_out_of_scope: [], chunks: [if\(], definitions: {}, errors: [], indentations: [<indent 2, open 133, close 296>, <indent 1, open 60, close 304>], is_resolved: True;
          statements_list
            scope_name_statement        InputString str: , is_out_of_scope: [], chunks: [if.statement.definition], definitions: {}, errors: [], indentations: [<indent 2, open 133, close 296>, <indent 1, open 60, close 304>], is_resolved: False;
          statements_list
            push_statement
              indentation_block
                statements_list
                  meta_scope_statement  InputString str: , is_out_of_scope: [], chunks: [if.statement.body], definitions: {}, errors: [], indentations: [<indent 2, open 133, close 296>, <indent 1, open 60, close 304>], is_resolved: False;
                statements_list
                  match_statement
                    InputString str: \), is_out_of_scope: [], chunks: [\)], definitions: {}, errors: [], indentations: [<indent 2, open 133, close 296>, <indent 1, open 60, close 304>], is_resolved: True;
                    statements_list
                      scope_name_statement      InputString str: , is_out_of_scope: [], chunks: [if.statement.definition], definitions: {}, errors: [], indentations: [<indent 2, open 133, close 296>, <indent 1, open 60, close 304>], is_resolved: False;
                    statements_list
                      pop_statement     InputString str: , is_out_of_scope: [], chunks: [true], definitions: {}, errors: [], indentations: [<indent 2, open 133, close 296>, <indent 1, open 60, close 304>], is_resolved: False;

Generating 'main_formatter.html'...
Generating 'main_formatter_syntax_tree.png'...
Generating 'main_formatter_abstract_syntax_tree.png'...
\end{minted}
\end{code}

@@

\begin{code}
\caption{Resultado da execução do arquivo ``source/main\_highlighter.py''}
\label{MainHighlighterPyResult}
\begin{minted}{text}
$ python3 main_highlighter.py
Syntax Tree
language_syntax
  preamble_statements
    master_scope_name_statement
      free_input_string
        text_chunk_end  [@1,7:16='source.sma'<TEXT_CHUNK_END_>,1:8]
    target_language_name_statement
      free_input_string
        text_chunk_end  [@2,24:48='Abstract Machine Language'<TEXT_CHUNK_END_>,2:7]
  language_construct_rules
    indentation_block
      enter_block       [@3,60:60='{'<OPEN_BRACE>,3:11]
      statements_list
        match_statement
          braced_free_input_string
            braced_text_chunk_end       [@4,73:74='//'<BRACED_TEXT_CHUNK_END_>,4:12]
          statements_list
            scope_name_statement
              free_input_string
                text_chunk_end  [@5,93:109='comment.start.sma'<TEXT_CHUNK_END_>,5:16]
          statements_list
            push_statement
              indentation_block
                enter_block     [@6,125:125='{'<OPEN_BRACE>,6:15]
                statements_list
                  meta_scope_statement
                    free_input_string
                      text_chunk_end    [@7,151:166='comment.line.sma'<TEXT_CHUNK_END_>,7:25]
                statements_list
                  match_statement
                    braced_free_input_string
                      braced_text_chunk_end     [@8,187:191='\\n|\\$'<BRACED_TEXT_CHUNK_END_>,8:20]
                    statements_list
                      pop_statement
                        free_input_string
                          text_chunk_end        [@9,216:219='true'<TEXT_CHUNK_END_>,9:22]
                leave_block     [@10,243:243='}'<CLOSE_BRACE>,11:9]
      leave_block       [@11,251:251='}'<CLOSE_BRACE>,13:1]

Abstract Syntax Tree
language_syntax
  preamble_statements
    master_scope_name_statement InputString str: , is_out_of_scope: [], chunks: [source.sma], definitions: {}, errors: [], indentations: [<indent 2, open 125, close 243>, <indent 1, open 60, close 251>], is_resolved: False;
    target_language_name_statement      InputString str: , is_out_of_scope: [], chunks: [Abstract Machine Language], definitions: {}, errors: [], indentations: [<indent 2, open 125, close 243>, <indent 1, open 60, close 251>], is_resolved: False;
  language_construct_rules
    indentation_block
      statements_list
        match_statement
          InputString str: //, is_out_of_scope: [], chunks: [//], definitions: {}, errors: [], indentations: [<indent 2, open 125, close 243>, <indent 1, open 60, close 251>], is_resolved: True;
          statements_list
            scope_name_statement        InputString str: , is_out_of_scope: [], chunks: [comment.start.sma], definitions: {}, errors: [], indentations: [<indent 2, open 125, close 243>, <indent 1, open 60, close 251>], is_resolved: False;
          statements_list
            push_statement
              indentation_block
                statements_list
                  meta_scope_statement  InputString str: , is_out_of_scope: [], chunks: [comment.line.sma], definitions: {}, errors: [], indentations: [<indent 2, open 125, close 243>, <indent 1, open 60, close 251>], is_resolved: False;
                statements_list
                  match_statement
                    InputString str: \n|$, is_out_of_scope: [], chunks: [\n|\$], definitions: {}, errors: [], indentations: [<indent 2, open 125, close 243>, <indent 1, open 60, close 251>], is_resolved: True;
                    statements_list
                      pop_statement     InputString str: , is_out_of_scope: [], chunks: [true], definitions: {}, errors: [], indentations: [<indent 2, open 125, close 243>, <indent 1, open 60, close 251>], is_resolved: False;

Generating 'main_highlighter.html'...
Generating 'main_highlighter_syntax_tree.png'...
Generating 'main_highlighter_abstract_syntax_tree.png'...
\end{minted}
\end{code}

>>>>

\begin{code}
\caption{Resultado da execução do arquivo ``source/main\_formatter.py''}
\label{MainFormatterPyResult}
\inputminted{text}{aftertext/main_formatter_output.txt}
\end{code}

@@

\begin{code}
\caption{Resultado da execução do arquivo ``source/main\_highlighter.py''}
\label{MainHighlighterPyResult}
\inputminted{text}{aftertext/main_highlighter_output.txt}
\end{code}
